Eigenvalues

### 2025-12-28 Code/R/Research/Eigenvalues.Rmd
Add time complexity section
Fix tmssa decomposition neig parameter

# Noise eigenvalues
```{r}
set.seed(5)
# N <- 19; L <- 7
# N <- 967; L <- 443
N <- 967; L <- 484
# N <- 19; L <- 10
P <- 2
K <- N - L + 1
noise <- matrix(rnorm(N * P), ncol = P)
noise_tens <- tens3(noise, L, "mssa")
noise_tens_fnorm <- fnorm_complex(tens3(noise, L, "mssa"))
sd_est <- sqrt(mean(noise^2))
sd_tens_est <- sqrt(mean(noise_tens@data^2))
ev <- noise |> tens_mssa_decompose(L, svd.method = "primme", neig=484, status = FALSE) |>
      get_tensor_eigenvalues()
ev_sums <- ev |> sapply(\(x) sum(x^2)) |> sqrt()

ssa_ev <- ssa(noise, L, kind = "mssa", neig=484)$sigma
ssa_ev_sum <- sqrt(sum(ssa_ev^2))

@@

P <- 2
# P <- 4
# P <- 8
# P <- 12
# P <- 16
# P <- 20
# P <- 40
P_case <- sprintf("_c%d", P)

@@

# A <- matrix(rnorm(P * S.true), nrow = P)
# A_case <- "_da"
A <- matrix(seq(-2, 2, length.out = P * S.true), nrow = P)
A_case <- "_ua"
# A <- matrix(rep(1, P * S.true), nrow = P)
# A_case <- "_ea"

poly.true <- 1 %o% rep(1, P) %o% rep(1, S.true)
poly_case <- ""
# poly.true <- c(1, 1) * matrix(runif(2 * P, 0.5, 2), nrow = 2) %o% rnorm(S.true, mean = 1, sd = 0.25)
# poly_case <- sprintf("p%d", dim(poly.true)[1] - 1)

phases.true <- matrix(rep(0, P * S.true), nrow = P)
phases_case <- "_ep"

@@

## All eigenvalues of the signal for particular L:
# get_tensor_eigenvalues(tens_mssa_decompose(signal, L, "hosvd", status = FALSE))
```

>>>>

# Noise eigenvalues
```{r}
set.seed(5)
# N <- 19; L <- 7
# N <- 967; L <- 443
# N <- 967; L <- 484
# N <- 19; L <- 10
N <- 99
L <- 20
P <- 20
K <- N - L + 1
noise <- matrix(rnorm(N * P), ncol = P)
noise_tens <- tens3(noise, L, "mssa")
noise_tens_fnorm <- fnorm_complex(tens3(noise, L, "mssa"))
sd_est <- sqrt(mean(noise^2))
sd_tens_est <- sqrt(mean(noise_tens@data^2))
ev <- noise |> tens_mssa_decompose(L, neig = c(L, K, P), status = FALSE) |>
      get_tensor_eigenvalues()
ev_sums <- ev |> sapply(\(x) sum(x^2)) |> sqrt()

ssa_ev <- ssa(noise, L, kind = "mssa", neig = L)$sigma
ssa_ev_sum <- sqrt(sum(ssa_ev^2))

@@

# P <- 2
# P <- 4
# P <- 8
# P <- 12
# P <- 16
# P <- 20
P <- 40
P_case <- sprintf("_c%d", P)

@@

# A <- matrix(rnorm(P * S.true), nrow = P)
# A_case <- "_da"
# A <- matrix(seq(-2, 2, length.out = P * S.true), nrow = P)
# A_case <- "_ua"
A <- matrix(rep(1, P * S.true), nrow = P)
A_case <- "_ea"

poly.true <- 1 %o% rep(1, P) %o% rep(1, S.true)
poly_case <- ""
# poly.true <- c(1, 1) * matrix(runif(2 * P, 0.5, 2), nrow = 2) %o% rnorm(S.true, mean = 1, sd = 0.25)
# poly.true <- c(1, 1, 1) * matrix(runif(3 * P, 0.5, 2), nrow = 3) %o% rnorm(S.true, mean = 1, sd = 0.25)
# poly.true <- c(1, 1) * matrix(1:(2*P), nrow = 2) %o% rnorm(S.true, mean = 1, sd = 0.25)
# poly_case <- sprintf("p%d", dim(poly.true)[1] - 1)

# phases.true <- matrix(rep(0, P * S.true), nrow = P)
# phases_case <- "_ep"
phases.true <- rep(1, P) %o% runif(S.true, 0, 2 * pi)
phases_case <- "_dp"

@@

## All eigenvalues of the signal for particular L:
L <- (N + 1) %/% 2
get_tensor_eigenvalues(tens_mssa_decompose(signal, L, "hosvd", status = FALSE))
```
